### 2015-05-27 test-proto.tex
Bastien's remarks

\section{Experimental setup}
The experimental environment is built around a standard x86 host and an ARM Cortex-A9 alongside an Altera Cyclone V FPGA as the target.
Both are linked toghether through a network capped by 100Mbps switches.
Both stations have gigabits ethernet interface and could hence be diretly connected to each other, but in that case the communication would be limited by the I/O transfers of the storage units -- a hard drive disk in one case, an micro-SD card in the second -- on which we can not depend to set a constant throughput limitation, as it is highly influenced by the data block size and general health of the support.

@@

@@

\section{TLS Connections}
This benchmark is done only with OpenVPN.
Since there is no standard support for those operation in the kernel yet, it would not have made sense to use IPsec, since it would have had to fallback to OpenSSL, then following the same path as OpenVPN do.
As soon as the public key operations can be plugged into the crypto API, this use case should however be tested.

For this use case, the board is configured in server mode, so that it can accept connections from any client.
The virtual machine will then execute then clients in parallel using the script~\ref{list:openvpn-client-script}.
The only option differentiating the clients is their IP address and port number.
Otherwise, all the clients share the same basic configuration file (see listing~\ref{list:openvpn-config-client}), which tell them to renogociate a new connection every second.
Hence, if a connection could be made with no delay and if the processes scheduling were ideal, the server would have to address 600 connections per minute.

@@

\section{File transfer}
The file transfered is an un compressed block of 128MB of random data generated using the following command:
\begin{lstlisting}[language=bash]
  $ head -c $((1024*1024*128)) /dev/urandom > heavy.file
\end{lstlisting}

For OpenSSH, the commmand \texttt{scp} will be used to transfer the data securely over an SSH tunnel.
As for OpenVPN and IPsec, a tunnel will be established beforehand, and then the simple \texttt{ftp} command will allow the client to fetch the file on the server.

>>>>

\section{Experimental setup}
The experimental environment is built around a standard x86 host and an ARM Cortex-A9 alongside an Altera Cyclone V FPGA as the target.
Both are linked toghether through a network capped by 100Mbps switches.
Both stations have gigabits ethernet interface and could hence be directly connected to each other, but in that case the communication would be limited by the I/O transfers of the storage units -- a hard drive disk in one case, an micro-SD card in the second -- on which we can not depend to set a constant throughput limitation, as it is highly influenced by the data block size and general health of the support.

@@

The table~\ref{tab:software-version} summarizes the softwares used and tjeir respective version.

\begin{table}
\center
\begin{tabular}{|l|l|} \hline
OpenVPN & 2.3.6 \\ \hline
OpenSSL & 1.0.2a \\ \hline
Strongswan & 5.3.0 \\ \hline
OpenSSH & 6.7p1 \\ \hline
\end{tabular}
\caption{Software used for the test}{note that OpenSSH was updated with the patch in appendix~\ref{chap:openssh-patch}.}
\label{tab:software-version}
\end{table}

@@

\section{TLS Connections}
This benchmark is done only with OpenVPN 2.3.6.
Since there is no standard support for those operation in the kernel yet, it would not have made sense to use IPsec, since it would have had to fallback to OpenSSL, then following the same path as OpenVPN do.
As soon as the public key operations can be plugged into the Linux Crypto API, this use case should however be tested.

For this use case, the board is configured in server mode, so that it can accept connections from any client.
The server does not connect with a specific client and waits for incomming connection requests (see listing~\ref{list:openvpn-server}).
The virtual machine will then execute then clients in parallel using the script~\ref{list:openvpn-client-script}.
The only option differentiating the clients is their IP address and port number.
Otherwise, all the clients share the same basic configuration file (see listing~\ref{list:openvpn-client}), which tell them to renogociate a new connection every second.
Hence, if a connection could be made with no delay and if the processes scheduling were ideal, the server would have to address 600 connections per minute.

@@

\section{File transfer}
The file transfered is an uncompressed block of 128MB of random data generated using the following command:
\begin{lstlisting}[language=bash]
  $ head -c $((1024*1024*128)) /dev/urandom > heavy.file
\end{lstlisting}~\newline{}

For OpenSSH, the commmand \texttt{scp} will be used to transfer the data securely over an SSH tunnel.
As for OpenVPN and IPsec, a tunnel will be established beforehand, and then the simple \texttt{ftp} command will allow the client to fetch the file on the server.
In order to use custom temporary security configuration with \texttt{scp}, the following command can be used:
\begin{lstlisting}[language=bash]
  $ ./scp -S /path/to/patched_openssh/bin/ssh -o Ciphers=aes256-cbc -o MACs=none@barco.com root@150.158.232.241:heavy.file .
\end{lstlisting}~\newline{}
